---
title: "Problem Set"
author: "Antunes Dantas"
date: "22-02-2017"
output: html_document
---

Quiz: Diamonds

  Passos: Carregar o pacote ggplot2 (pois é nele que vem os pacote de dados diamonds), carregar o pacote diamonds, summary para mostrar os detalhes do pacote, ?diamonds para mostrar a documentação.

```{r}
library(ggplot2)
data(diamonds)
summary(diamonds)
?diamonds
```

Quiz: Price Histogram

```{r}
qplot(data = diamonds, x = diamonds$price)
```

Quiz: Diamond Counts

```{r}
sum(diamonds$price < 500)
sum(diamonds$price < 250)
sum(diamonds$price >= 15000)
```

Quiz: Cheaper Diamonds

```{r}
qplot(data = diamonds, x = diamonds$price, binwidth = 30,
      color = I('black'), fill = I('#099DD9')) +
  scale_x_continuous(lim = c(326, 1100))
```

Quiz: Price By Cut Histograms

```{r}
qplot(data = diamonds, x = diamonds$price,
      color = I('black'), fill = I('#099DD9')) +
  scale_x_continuous(lim = c(326, 18820)) +
  facet_wrap(~cut)
```

Quiz: Price By Cut

```{r}
by(diamonds$price, diamonds$cut, summary)
by(diamonds$price, diamonds$cut, max)
by(diamonds$price, diamonds$cut, min)
```

Quiz: Scales and Multiple Histograms

```{r}
qplot(x = price, data = diamonds) + facet_wrap(~cut, scales = "free_y")
```

Quiz: Price per Carat by Cut

```{r}
qplot(data = diamonds, x = diamonds$price * diamonds$carat,
      color = I('black'), fill = I('#099DD9')) +
  scale_x_log10() +
  facet_wrap(~cut)
```

Quiz: Price Box Plots

```{r}
qplot(geom = 'boxplot',
      data = diamonds,
      y = diamonds$price,
      x = diamonds$cut) +
  coord_cartesian(ylim = c(326, 18820))
```

Quiz: Interquartile Range - IQR

```{r}
summary(subset(diamonds, color == "D"))
IQR(subset(diamonds, color == "D")$price)
IQR(subset(diamonds, color == "J")$price)
```

Quiz: Price per Carat Box Plots by Color

```{r}
qplot(geom = 'boxplot',
      data = diamonds,
      x = diamonds$color,
      y = diamonds$price/diamonds$carat)
```

Quiz: Carat Frequency Polygon

```{r}
qplot(geom = 'freqpoly',
      data = diamonds,
      x = diamonds$carat, binwidth = .1) +
  scale_x_continuous(breaks = c(0.1, 0.3, 0.8, 1.01, 1.6, 2.0, 3.0, 5.0))
```


